---
params:
   epoch: NULL
   metrics: NULL
   ctable: NULL
   aoi: NULL
   dpath: "../requests"
pagetitle: Geranium instant report
title: Geranium Instant Report
author1: Boris Solovyev, Nikita Platonov
date: ""
date1: "`r as.POSIXlt(Sys.time())`"
link-citations: true
csl1: https://nplatonov.github.io/platt4.csl
output:
   bookdown::html_document2:
      base_format: rmarkdown::html_vignette
      css: https://nplatonov.github.io/site_libs/html_vignette.css
      lib_dir: "`r params$dpath`"
      self_containded: false
      number_sections: no
   bookdown::word_document2:
      toc: false
      number_sections: false
      reference_docs: instant-ref.docx
   bookdown::pdf_document2:
      toc: false
      number_sections: false
   pdf_document:
      fig_caption: false
   pinp::pinp: default
   rticles::agu_article: default
   tint::tintPdf: default
   tufte::tufte_handout:
      latex_engine: xelatex
   html_fragment: default
---

```{r mem1, eval=FALSE, echo=FALSE}
print(lobstr::mem_used())
```

```{r workingir, eval=!ursa:::.isShiny(), include=FALSE}
# print(lobstr::mem_used())
.wd <- setwd("..")
source("resources/header.R")
setwd(.wd)
rm(.wd)
```

```{r memory, include=FALSE}
trackMemory <- T & !ursa:::.isShiny() & staffOnly
gcMemory <- F & trackMemory
```

`r if (staffOnly) paste(packageVersion("ursa"),packageVersion("sf"))`

```{r setup, include=TRUE,echo=FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
isPlotly <- FALSE
aoi <- params$aoi
metrics <- params$metrics
ctable <- params$ctable
dpath <- params$dpath
epoch <- params$epoch
filetype <- knitr::opts_knit$get("rmarkdown.pandoc.to")
knitr::opts_chunk$set(if (!grepl("docx",filetype)) fig.align="center" else NULL
                     ,fig.width=6,fig.height=3.6
                     ,widgetframe_widgets_dir=dpath
                     ,echo=trackMemory,message=F,warning=F
                     )
invisible(file.remove(dir(path=dpath,pattern="^orca.+\\.(pdf|png)$",full.names=TRUE,recursive=TRUE)))
if (isPlotly) require(plotly,quietly=TRUE) else require(ggplot2,quietly=TRUE)
if (!isPlotly)
   p0 <- theme_minimal()+
      theme(axis.text.x = element_text(angle=90)
           ,panel.grid.minor.x = element_blank()
           ,panel.grid.major.x = element_blank()
           )   
if (F) {
   print(lobstr::mem_used())
   ursa:::.gc(gcMemory)
   getwd()
}
```

```{r publish, eval=T, echo=F, include=trackMemory}
'publish' <- function(p) {
   if (inherits(p,"ggplot")) {
      ret <- p
   }
   else if (inherits(p,"plotly")) {
      if (filetype %in% "latex") {
         if (TRUE) {
            fs <- 18
            p <- plotly::layout(p
                               ,title=list(font=list(size=fs))
                               ,legend=list(font=list(size=round(0.9*fs)))
                               ,xaxis=list(tickfont=list(size=fs),titlefont=list(size=fs))
                               ,yaxis=list(tickfont=list(size=fs),titlefont=list(size=fs))
                               )
         }
        # if (FALSE) { 
        #    opW <- options(warn=-10)
        #    ret <- plotly::export(p)
        #    options(opW)
        # }
         if (nchar(Sys.which("ZZZorca"))) {
            if (!dir.exists(dpath))
               dir.create(dpath,recursive=TRUE)
            fileout <- file.path(dpath,basename(tempfile(pattern="orca",fileext=".pdf")))
            plotly::orca(p,fileout)
            ret <- knitr::include_graphics(fileout)
         }
         else {
            ret <- NULL
            if (F) {
               if (!dir.exists(dpath))
                  dir.create(dpath,recursive=TRUE)
               fileout <- file.path(dpath,basename(tempfile(pattern="orca",fileext=".png")))
               ret <- try(plotly::plotly_IMAGE(p,width=800,height=600,scale=1,out_file=fileout))
               if (!inherits(ret,"try-error"))
                  ret <- knitr::include_graphics(fileout,dpi=300)
               else
                  ret <- NULL
            }
            if (is.null(ret)) {
               opW <- options(warn=-10)
               ret <- plotly::export(p)
               options(opW)
            }
         }
      }
      else
         ret <- p
   }
  # on.exit({ursa:::.gc(gcMemory);print(lobstr::mem_used())})
   ret
}
```

```{r aoi, eval=T, include=trackMemory}
if (!isShiny & is.null(aoi)) {
   aoi <- selectRegion("PAC 22")
}
```

```{r ctable, eval=T, include=trackMemory}
if (is.null(ctable)) {
   group <- NULL # c("\\d")
   ctable <- crossTable(aoi=aoi,group=group,minCover=3)
}
if (!is.null(ctable)) {
   if (filetype=="latex") {
      ctable[["CF name"]] <- gsub("<em>","\\\\emph{",ctable[["CF name"]])
      ctable[["CF name"]] <- gsub("</em>","}",ctable[["CF name"]])
   }
   else {
      ctable[["CF name"]] <- gsub("<em>","*",ctable[["CF name"]])
      ctable[["CF name"]] <- gsub("</em>","*",ctable[["CF name"]])
   }
}
```

```{r metrics, eval=T, include=trackMemory}
if ("result" %in% names(metrics)) {
   metrics <- metrics$result
}
if (is.null(metrics)) {
   m1 <- regionStats(aoi=aoi,ctable=ctable,raw=F,isPA=F)
   m2 <-  regionActivityIndices(aoi=aoi,ctable=ctable,extended=TRUE)
   metrics <- if (T) c(m1,m2) else if (F) m1 else if (F) m2 else NULL
  # saveRDS(names(metrics),"C:/tmp/instantReport.rds")
  # stop("A")
}
isConcern <- "NACB" %in% names(metrics)
isAction <- "CAB" %in% names(metrics)
```
```{r deprecated, eval=F, include=trackMemory}
if ("result" %in% names(metrics)) {
   metrics <- metrics$result
   ctable <- crossTable(aoi=aoi
                       ,group=names(metrics$CFNAC)
                       ,season=names(metrics$seasonNAC)
                       ,activity=names(metrics$industryNAC)
                       )
}
```
```{r label, eval=T, include=trackMemory}
isAOI <- is_spatial(aoi)
if (isAOI) {
   if ("id" %in% spatial_colnames(aoi))
      lab <- regionSF[[aoi$region[1]]]$region[aoi$id]
   else
      lab <- aoi$region
   if (is.null(lab))
      lab <- "Custom Selection"
   if (length(lab)>1)
      lab <- paste(lab,collapse=", ")
} else {
   lab <- "ArcNet domain"
}
# str(list(aoi=aoi,metrics=metrics,ctable=ctable,dpath=dpath))
```

## Instant Report for `r lab`.

```{r paoi, include=trackMemory, eval=TRUE}
# print(lobstr::mem_used())
paoi <- spatial_union(puAOI(aoi))
if (!isAOI) {
   paoi <- ursa:::spatialize(paoi,resetGrid=TRUE,resetProj=TRUE)
} else {
   paoi <- ursa:::spatialize(paoi,resetGrid=TRUE,resetProj=TRUE,style=6931)
}
# print(lobstr::mem_used())
```

```{r preselectional, include=trackMemory, eval=!FALSE}
gAOI <- session_grid(paoi,expand=1.5)
# print(lobstr::mem_used())
compose_open()
panel_new("white")
if (T) {
   if (isAOI) {
     # print(lobstr::mem_used())
      ct1 <- panel_plot(sf::st_cast(paoi,"MULTILINESTRING"),lwd=1)
     # print(lobstr::mem_used())
      if (F) {
         gaoi <- spatial_geometry(aoi)
         ct2 <- panel_plot(gaoi,lwd=0.1)
         rm(gaoi)
      }
      else {
        # print(lobstr::mem_used())
         ct2 <- panel_plot(spatial_geometry(aoi),lwd=0.1)
        # print(lobstr::mem_used())
      }
   } else {
      ct1 <- panel_plot(paoi,lwd=0.1)
      ct2 <- NULL
   }
}
# print(lobstr::mem_used())
panel_decor(coast.fill="#00000010")
# print(lobstr::mem_used())
if (T) {
   if (T) {
      ursa:::panel_legend(list('Gridded (PUs) selection'=ct1,'Original selection'=ct2))
   } else {
      if (isAOI)
         NULL
      else
         legend("bottomright",legend=c('Gridded (PUs) selection','Original selection'))
   }
}
ret <- compose_close()
# rm(paoi)
# ursa:::.gc(gcMemory)
# print(lobstr::mem_used())
opW <- options(warn=0)
output <- try(knitr::include_graphics(ret))
options(opW)
if (F) {
   da <- lapply(search(),\(e) sapply(ls(e),\(x) object.size(get(x)))) |> unlist()
   da <- data.frame(object=names(da),size=unname(da))
   da <- da[order(da$size,decreasing=TRUE),]
   print(head(da,12))
   print(sum(da$size))
   rm(da)
   ursa:::.gc(gcMemory)
}
# print(lobstr::mem_used())

```

```{r selectional, fig.cap="Selected Area", eval=!FALSE}
output
```

```{r preMNSR, include=trackMemory, eval=F}
#ret <- display(a,ncolor=11,stretch="eq",pal=pYlRd,interval=TRUE)
#m <- !is.na(allocate(cAOI,resetGrid=TRUE))
paoi <- spatial_union(puAOI(aoi))
if (!isAOI) {
   paoi <- ursa:::spatialize(paoi,resetGrid=TRUE,resetProj=TRUE)
} else {
   paoi <- ursa:::spatialize(paoi,resetGrid=TRUE,resetProj=TRUE,style=6931)
}
session_grid(paoi,expand=1.2)
compose_open()
panel_new("white")
a <- polygonize(metricsMap(ctable=ctable)["NACR"])
ct3 <- panel_plot(a,ncolor=11,stretch="eq",pal=pYlRd,interval=TRUE)
rm(a)
ursa:::.gc(gcMemory)
if (T) {
   if (isAOI) {
      ct1 <- panel_plot(sf::st_cast(paoi,"MULTILINESTRING"),lwd=1)
   } else {
      ct1 <- panel_plot(paoi,lwd=0.1)
   }
}
# rm(paoi)
ursa:::.gc(gcMemory)
panel_decor(coast.fill="#00000010")
if (T) {
   ursa:::panel_legend(list('Gridded (PUs) selection'=ct1))
}
compose_legend(ct3)
ret <- compose_close()
opW <- options(warn=0)
output <- try(knitr::include_graphics(ret))
options(opW)
```

```{r MNSR, fig.cap="MNSR Index Distribution", eval=F}
output
```

`r if (isConcern) "Basic statistics of selected area:"`

```{r prebasic, include=trackMemory, eval=isConcern}
da <- with(metrics,data.frame('No of Pus'=nPU
                             ,'No of CFs'=nCF
                             ,'Total Area, km2'=area_src
                             ,'Total Area, PUs, km2'=area_pu
                             ,'Terrestrial Area, PUs, km2'=puLand
                             ,'Marine Area, PUs, km2'=puMarine
                             ,check.names=FALSE
                             ))
if (filetype %in% "latex") {
  # colnames(da) <- gsub("PUs"," $\\\\\\\\$ PUs",colnames(da))
   colnames(da) <- gsub("km2","km\\\\textsuperscript{2}",colnames(da))
} else {
   colnames(da) <- gsub("km2","km^2^",colnames(da))
}
```
```{r basic, eval=isConcern}
knitr::kable(da,caption="Basic statistics",escape=FALSE)
```

`r if (isConcern) "Concern Indexes:"`

```{r preconcern, include=trackMemory, eval=isConcern}
da <- regionConcernTables(metrics,type="raw")
if (nrow(da)==3)
   da <- cbind(da[3,1:2],da[1,3:4])
if (T) {
   colnames(da) <- c("RSC-PU","ROC-PU","RSC-AOI","ROC-AOI")
   colnames(da) <- paste0(colnames(da),", \\%")
}
rownames(da) <- NULL
colnames(da)
```

```{r concern, eval=isConcern}
knitr::kable(da,digits=1,escape=FALSE,caption="Concern Indexes")
```

`r if (isAction) "Pressure Indexes:"`


```{r preactivity, include=trackMemory, eval=isAction}
da <- regionActivityTables(ctable=ctable,aoi=aoi,epoch=epoch,type="raw") |> tail(1)
if (FALSE)
   colnames(da) <- c("CAPR, \\%","CAP, \\%","AAR, \\%")
if (TRUE)
   colnames(da) <- c("OIP-P, \\%","ROIP-AOI, \\%","AA-PU, \\%")
rownames(da) <- NULL
colnames(da)
```

```{r activity, eval=isAction}
knitr::kable(da,digits=1,escape=FALSE,caption="Pressure Indexes")
```

`r if (isConcern) "Relative Overall Concern Level by Month (ROC-M):"`

```{r preseasonalC, include=trackMemory, eval=isConcern}
p <- regionPlotSeasonConcern(metrics,relative=TRUE,plotly=FALSE)
```

```{r seasonalC, fig.cap="Relative Overall Concern Level by Month (ROC-M)", eval=isConcern}
publish(p+p0)
```

`r if (isAction) "Relative Overall Industrial Pressure by Month (ROIP-M):"`

```{r preseasonalA, include=trackMemory, eval=isAction}
p <- regionPlotSeasonActivity(metrics,relative=TRUE,plotly=FALSE)
```

```{r seasonalA, fig.cap="Relative Overall Industrial Pressure by Month (ROIP-M)", eval=isAction}
publish(p+p0)
```


`r if (isConcern) "Relative Overall Concern Level by Activity (ROC-IA):"`

```{r preindustryPlotC, include=trackMemory, eval=isConcern}
p <- regionPlotIndustryConcern(metrics,relative=TRUE,plotly=FALSE)
```

```{r industrialPlotC, fig.cap="Relative Overall Concern Level by Activity (ROC-IA)", eval=isConcern}
publish(p+p0)
```

`r if (isAction) "Relative Overall Industrial Pressure by Activity (ROIP-IA):"`

```{r preindustryPlotA, include=trackMemory, eval=isAction}
p <- regionPlotIndustryActivity(metrics,relative=TRUE,plotly=FALSE)
```

```{r industrialPlotA, fig.cap="Relative Overall Industrial Pressure by Activity (ROIP-IA)", eval=isAction}
publish(p+p0)
```

`r if (isConcern) "Relative Overall Concern Level of Activities:"`

```{r preindustryList, include=trackMemory, eval=isConcern}
#saveRDS(metrics,"C:/tmp/metric.rds")
v <- sort(metrics$industryNACB,decreasing=TRUE)
vname <- names(v)
da <- data.frame('Activity ID'=industryCode(vname)
                ,'Activity'=industryName(vname)
                ,'ROC-IA, %'=100*v ## MNSA
                ,check.names=FALSE)
rownames(da) <- NULL
```

```{r industryList, eval=isConcern}
knitr::kable(da,escape=TRUE,caption="List of Activities ordered by Relative Overall Concern Level by Activity",digits=1)
```

`r if (isConcern) "CF list by Relative Overall Concern Level:"`

```{r prebyNAC, include=trackMemory, eval=isConcern}
da <- ctable[,c("CF name","Cover","NAC")]
da <- da[order(da[["NAC"]],decreasing=TRUE),]
da <- cbind(CF=rownames(da),da)
colnames(da) <- c("CF ID","CF Name","Coverage, \\%","ROC-CF, \\%")
da <- da[,-3]
rownames(da) <- NULL
``` 

```{r byNAC, eval=isConcern}
knitr::kable(da,digits=1,escape=FALSE,caption="CF list by Relative Overall Concern Level")
```

Top CFs by Coverage (all with spatial presence in region (coverage) above 20%):

```{r prebyCover, include=trackMemory, eval=T}
if ((all(ctable$'CAP' %in% c("n/a","N/A")))&&(isAction)) {
   cap <- 100*metrics$CAA$capCF/metrics$CAB$capCF
   cap[is.na(cap)] <- 0
   ind <- match(rownames(ctable),names(cap))
   ctable$'CAP'[!is.na(ind)] <- round(cap[na.omit(ind)],1)
}
da <- ctable[,c("CF name","Cover",if (isConcern) "NAC",if (isAction) "CAP")]
da <- da[order(da[["Cover"]],decreasing=TRUE),]
da <- da[da[["Cover"]]>=20,]
da <- cbind(CF=rownames(da),da)
colnames(da) <- c("CF ID","CF Name","Coverage, \\%"
                 ,if (isConcern) "ROC-CF, \\%",if (isAction) "ROIP-CF, \\%"
                 )
rownames(da) <- NULL
```

```{r byCover, eval=T & nrow(da)>0}
knitr::kable(da,digits=1,escape=FALSE,caption="Top CFs by Coverage")
```

```{r mem2, eval=trackMemory, echo=trackMemory}
# print(lobstr::mem_used())
```


```{r NACR, include=trackMemory, eval=isConcern}
a <- indexNACR(aoi=aoi,ctable=ctable)
d6 <- map1_1d(a)
compose_open(layout=c(1,1+as.integer(isAOI)),legend="right")
panel_new("white")
panel_raster(d6)
if (isAOI)
   panel_plot(paoi,lwd=1,col="transparent")
panel_decor(coast.fill="#00000010")
if (isAOI) {
   g2 <- session_grid(consistent_grid(ursa_grid(gAOI)),ref=ursa_grid(d6))
   panel_new("white")
  # d6r <- ursa:::.gdalwarp(d6,grid=g2)
   d6r <- regrid(d6,resample=0)
   panel_raster(d6r)
   panel_plot(paoi,lwd=3,col="transparent")
   panel_decor(coast.fill="#00000010")
}
compose_legend(d6)
ret <- compose_close()
```

```{r plotNACR, eval=isConcern, fig.cap="OC-P distribution"}
knitr::include_graphics(ret,dpi=300)
```

```{r NAOR, include=trackMemory, eval=isConcern}
a <- indexNAOR(aoi=aoi,ctable=ctable)
d6 <- map1_1d(a)
compose_open(layout=c(1,1+as.integer(isAOI)),legend="right")
panel_new("white")
panel_raster(d6)
if (isAOI)
   panel_plot(paoi,lwd=1,col="transparent")
panel_decor(coast.fill="#00000010")
if (isAOI) {
   g2 <- session_grid(consistent_grid(ursa_grid(gAOI)),ref=ursa_grid(d6))
   panel_new("white")
  # d6r <- ursa:::.gdalwarp(d6,grid=g2)
   d6r <- regrid(d6,resample=0)
   panel_raster(d6r)
   panel_plot(paoi,lwd=3,col="transparent")
   panel_decor(coast.fill="#00000010")
}
compose_legend(d6)
ret <- compose_close()
```

```{r plotNAOR, eval=isConcern, fig.cap="SC-P distribution"}
knitr::include_graphics(ret,dpi=300)
```

```{r CAPR, include=trackMemory, eval=isAction}
a <- indexCAPR(aoi=aoi,ctable=ctable,epoch=epoch)
d6 <- map1_1d(a)
compose_open(layout=c(1,1+as.integer(isAOI)),legend="right")
panel_new("white")
panel_raster(d6)
if (isAOI)
   panel_plot(paoi,lwd=1,col="transparent")
panel_decor(coast.fill="#00000010")
if (isAOI) {
   g2 <- session_grid(consistent_grid(ursa_grid(gAOI)),ref=ursa_grid(d6))
   panel_new("white")
  # d6r <- ursa:::.gdalwarp(d6,grid=g2)
   d6r <- regrid(d6,resample=0)
   panel_raster(d6r)
   panel_plot(paoi,lwd=3,col="transparent")
   panel_decor(coast.fill="#00000010")
}
compose_legend(d6)
ret <- compose_close()
```

```{r plotCAPR, eval=isAction, fig.cap="OIP-P distribution"}
knitr::include_graphics(ret,dpi=300)
```

```{r HumanUse, include=trackMemory, eval=isAction}
a <- indexHumanUse(aoi=aoi,ctable=ctable,epoch=epoch)
d6 <- map1_1d(a)
compose_open(layout=c(1,1+as.integer(isAOI)),legend="right")
panel_new("white")
panel_raster(d6)
if (isAOI)
   panel_plot(paoi,lwd=1,col="transparent")
panel_decor(coast.fill="#00000010")
if (isAOI) {
   g2 <- session_grid(consistent_grid(ursa_grid(gAOI)),ref=ursa_grid(d6))
   panel_new("white")
  # d6r <- ursa:::.gdalwarp(d6,grid=g2)
   d6r <- regrid(d6,resample=0)
   panel_raster(d6r)
   panel_plot(paoi,lwd=3,col="transparent")
   panel_decor(coast.fill="#00000010")
}
compose_legend(d6)
ret <- compose_close()
```

```{r plotHumanUse, eval=isAction, fig.cap="Cumulative amount of industrial activity"}
knitr::include_graphics(ret,dpi=300)
```
