---
runtime: shiny
pagetitle1: Compatibility with AOIs
pagetitle2: Compatibility with AOIs - WWF ArcNet
pagetitle3: Decision Support and Engagement Prioritisation
pagetitle4: Soiga
pagetitle5: <a class="home" href="#">Geranium NG</a>
pagetitle: Geranium NG
author6: 
author5: "<abbr title=\"Tab panel with subtitle have to fill one line. Subtitle: 'Decision support and engagement prioritisation and visualisation tool for the Arctic Seas conservation planners'\">De...</abbr>"
author4: Decision support and engagement prioritisation
author3: Decision support and engagement prioritisation and visualisation tool for the Arctic Seas conservation planners
author2: 🏭🚢🎣🛢 Human use ⚔ Conservation 🐳🐻🐟🐚
author1: "[WWF ArcNet](https://arcticwwf.org/work/ocean/arcnet/)"
zzzpagetitle: Compatibility with AOIs
link-citations: yes
output1: html_document
output:
   flexdashboard::flex_dashboard:
      theme: yeti
      theme2: 
         version: 4
         bootswatch: minty
      logo: https://wwf.ru/assets/img/logo.jpg
      favicon: https://www.arcticwwf.org/favicons/favicon-32x32.png
      orientation: columns
      vertical_layout: fill
      mathjax: ~
      css:
      - site_libs/common.css
      - site_libs/flex_dashboard.css
      - include/geranium.css
      css1:
      - https://nplatonov.github.io/site_libs/common.css
      - https://nplatonov.github.io/site_libs/flex_dashboard.css
      - include/geranium.css
      navbar:
         - { icon: "ion-home", href: "#", align: right}
         - { icon: "ion-help", href: "#section-welcome", align: right}
         - { icon: "fa-github", href: "https://github.com/nplatonov/geranium", align: right, target: _blank}
         - { title: "WWF<sup>®</sup> ArcNet", zzzicon: "fa-info-circle", href: "https://arcticwwf.org/work/ocean/arcnet/", align: right, target: _blank}
output3:
   html_vignette: 
      css:
      - https://nplatonov.github.io/site_libs/common.css
      - https://nplatonov.github.io/site_libs/html_vignette.css
---

```{r init643ce921796fb94ae61005778a47b7fe, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE)
```

```{js, eval=T}
const item = document.getElementsByClassName("navbar-brand");
const text = item[0].firstChild;
const link = document.createElement('a');
const cl = document.createElement('span');
link.setAttribute("href","#");
link.appendChild(text);
cl.setAttribute("class","navbar-title");
cl.appendChild(link);
item[0].appendChild(cl);
const item2 = document.getElementsByClassName("navbar-author");
item[0].appendChild(item2[0]);
```

```{r header, eval=F, code=readLines("resources/header.R")}
```

```{r server, code=readLines("resources/server.R")}
```

```{r client, code=readLines("resources/client.R")}
```

```{r tabs}
hideTabs <- !is.null(rmarkdown::metadata[["author"]])
```

# Spatial query {#map data-orientation="columns" data-height=1900 `r if (hideTabs) ".hidden"`}

## {.mainbar}

### Map to select/edit regions {data-width=500 data-height=200}

```{r, eval=T & isShiny}
uiOutput("uiMap")
#leafletOutput("viewer")
#editModUI("editor")
#selectModUI("selector")
```

```{r eval=T & isShiny, fig.height=800}
output$uiMap <- renderUI({ ## editor-editModUI / selector-selectModUI / viewer-leafletOutput
   cat("renderUI -- begin:\n")
   if (input$region %in% nameEditor) {
      Sys.sleep(1)
      ret <-  editModUI("editor")
      Sys.sleep(1)
   }
   else if (T & input$predefined %in% nameClick) {
      ret <-  selectModUI("selector")
   }
   else { ## selected from list: "PAC "
      ret <- leafletOutput("viewer")
     # ret <- textOutput("note")
   }
   cat("renderUI -- end:\n")
   ret
})
```

```{r eval=F & isShiny}
output$viewer <- renderLeaflet({
   mapViewer()
})
```

<!--
https://github.com/rstudio/flexdashboard/issues/181
-->

<!--
> [Conservation Action Hotspots](#welcome) &nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [How the assessment was made](#welcome) &nbsp;&nbsp;&nbsp;&nbsp; [Dictionary](#welcome) &nbsp;&nbsp;&nbsp;&nbsp; [FAQ](#welcome)
-->


## {#inputs .no-sidebar zzzdata-width="470px" data-width=300}

### {data-height="auto"}


```{r, eval=isShiny}
width <- c("100%","450px")[2]
if (F)
   checkboxInput("customize","Customize",value=FALSE)
if (F)
   shiny::selectInput("sheet","Human use",nameInit,width=width)
if (F)
   shiny::selectInput("column","Industry",nameInit,width=width)
fillRow(flex=NA
   ,selectInput("region","Spatial query",c(names(regionSF),nameEditor)
              ,selected="PACs" # sample(names(regionSF),1)
              ,width="272px")
   ,HTML("&nbsp;&nbsp;")
   ,conditionalPanel(condition=paste0("input.xxxregion==",sQuote(nameEditor)) ## nameEditor <- "Editor"
      ,selectInput("predefined","Region from list",nameInit
                   # ,selected=nameSelector
                    ,width="172px")
   )
   ,sliderInput("omitPercent"
             # ,list(content = "My Label", position = "left")
              ,label="Omit small coverage"
              ,min=0,max=5,step=0.1,value=0
              ,width="172px"
              )
)
fillRow(flex=c(NA,NA,NA,NA,NA)
   ,selectInput("group","CF group",unname(groupList)
             # ,selected=sample(unname(groupList),1)
              ,selected=unname(ifelse(F,sample(groupList,1),groupList[1]))
              ,multiple=T
             # ,selected="Cetaceans"
              ,width="181px")
   ,HTML("&nbsp;&nbsp;")
   ,selectInput("season","Season",seasonList
             # ,selected=ifelse(devel,sample(seasonList,1L),seasonList[1L])
              ,selected=seasonList[1L]
              ,width="136px")
   ,HTML("&nbsp;&nbsp;")
   ,selectInput("activity","Activity",c(nameAllHuman,names(industries))
              # ,selected=ifelse(devel,sample(seasonList,1L),seasonList[1L])
              # ,selected=seasonList[1L]
               ,selected=nameAllHuman
               ,multiple=T
               ,width="121px")
   )
```

---


```{r, eval=isShiny}
if (T)
   shiny::selectInput("industry","Industry (only for visualization)"
                    # ,c('No overlap'="none",'All human use'="all",industries)
                     ,"---"
                     ,multiple=T
                     ,width=width)
   conditionalPanel(condition="input.industry!='none'"
      ,fillRow(flex=c(NA,1,NA)
         ,selectInput("coloring","Colorization",unname(methodList)
                   # ,selected=grep("overlap",methodList,value=TRUE)
                    ,width="312px")
         ,HTML("&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;")
         ,actionLink("drawIndustry","Update map")
      )
   )
if (F) {
  shiny::actionButton(inputId='ab1', label="location.href", 
                          icon = icon("th"), 
                          onclick ="location.href='#section-region';"
                          )
  shiny::actionButton(inputId='ab2', label="window.open", 
                          icon = icon("th"), 
                          onclick ="window.open('#section-region', '_top')"
                         # onclick ="location.href('#section-region')"
                          )
}
```

```{r, eval=T}
renderUI({
   aoi <- rvAOI()
   lab <- regionSF[[input$region]]$region[aoi$id]
   if (length(lab)>1)
      lab <- "Overview for selected regions"
   else
      lab <- paste("Overview for",dQuote(lab),"region")
   if (is.null(aoi))
      b2 <- navButton("Global metrics","#descRegion","desc",span=T)
   else
      b2 <- navButton(lab,"#descRegion","desc",span=T)
   b1 <- navButton("Selected Area Details","#crosstable","cross",span=T)
   b <- if (is.null(aoi)) list(b1,b2) else list(b1,b2)
   navButton(b,border=T)
})
```

<!--
### {data-height="auto"}
-->

```{r, eval=FALSE}
renderUI({
   col <- if (!is.null(rvSelectIndustry())) "grey" else "grey"
   navButton("Customise my choice","#trafficlight",col,border=TRUE)
})

```{r, eval=F}
renderUI({
   lab0 <- "Human activity"
   aoi <- rvAOI()
   if (is.null(aoi))
      lab <- paste(lab0,"in the Arctic")
   else {
      lab <- regionSF[[input$region]]$region[aoi$id]
      if (length(lab)>1)
         lab <- paste(lab0,"for selected regions")
      else
         lab <- paste(lab0,"for",dQuote(lab),"region")
   }
   col <- if (is.null(rvAOI())) "orange" else "orange"
   b1 <- navButton(lab,"#list",col,border=T)
  # b2 <- navButton("Conservation Features","#list",col,span=T)
  # navButton(list(b1,b2),border=T)
   b1
})
```
```{r, eval=T}
renderUI({
   col <- if (is.null(rvAOI())) "list" else "list"
  # b1 <- navButton("Human Activities in the Arctic","#list",col,span=T)
  # b2 <- navButton("Conservation Features","#list",col,span=T)
  # navButton(list(b1,b2),border=T)
   navButton("Lists of Human use and Conservations","#list",col="list",border=T)
})
##~ renderUI({
   ##~ col <- if (is.null(rvAOI())) "green" else "grey"
##~ })
```

---

<!--

[Industry cut (deprecated)](#industry)
&nbsp;&nbsp;&nbsp;&nbsp;
[Customise my choice (deprecated)](#trafficlight)
-->

```{r,eval=F,results='asis'}
fillRow(flex=c(1,1)
   ,renderUI({
      tagList(
         a("Conservation Action Hotspots",href="#welcome"),
         br(),
         a("How the assessment was made",href="#welcome"),
         br(),
         a("Dictionary",href="#welcome"),
         br(),
         a("FAQ",href="#welcome")
      )
   })
   ,if (F & staffOnly) renderPrint(selectionRegion()) else renderText("empty")
)
```

[Conservation Action Hotspots](#welcome)  
[How the assessment was made](#welcome)  
[Dictionary](#welcome)  
[FAQ](#welcome)  


```{r eval=T & isShiny & staffOnly, results='asis'}
cat("### {data-height=\"auto\"}\n\n")
renderPrint({
   selectionRegion()
})
```

# Selected Area Details {#crosstable style="position: relative;" .zzzno-mobile .zzzno-print data-orientation="rows" `r if (hideTabs) ".hidden"`}

## Row {style="height: 50pc;" data-height=300}

### {#tabcross zzzstyle="height: 50vh;" data-width=600}

```{r, eval=T}
fillCol(flex=c(NA,1)
      # ,textOutput("verb")
       ,DT::DTOutput("cross") # %>% shinycssloaders::withSpinner()
      # ,tableOutput("smpl")
       ,uiOutput("buttonsCross")
       )
```

```{r, eval=F}
output$verb <- renderText({
   paste0(sQuote("flexdashboard")," package version: "
         ,as.character(packageVersion("flexdashboard")))
})
```{r, eval=T}
output$cross <- DT::renderDT({
   tableCross()
})
```

```{r, eval=F}
output$smpl <- renderTable(res,align="r",rownames=TRUE)
```

```{r,eval=T}
output$buttonsCross <- renderUI({
   if (F)
      fillRow(flex=c(1,NA)
         ,sliderInput("omitPercent",label="Omit small coverage",min=0,max=10,step=0.1,value=0)
         ,buttonsCross()
      )
   buttonsCross()
})
```

```{r eval=staffOnly, results='asis'}
cat("### verbose {data-width=200}\n\n")
renderPrint(selectionTables())
```

# Conservation Feature Details {#annualCF data-orientation="columns" `r if (hideTabs) ".hidden"`}

## {data-width=500}

<!--
## Column {zstyle="height:100pc;" vertical_layout: scroll}
-->

### All compapibilities for a single CF

```{r eval=T & isShiny}
fillCol(flex=c(NA,1,NA,NA)
       ##~ ,shiny::selectInput("cfcode","CF from crosstable",nameInit,width=width)
      # ,selectInput("cfcode","Conservation Feature"
      #             ,choices=nameInit
                  # ,choices=cfmeta$label
                  # ,selected=sample(cfmeta$label,1)
      #             ,width="680px")
      # ,textOutput("crossCol")
      ##~ # ,htmlOutput('cflink')
       ,htmlOutput('cfmeta')
      # ,verbatimTextOutput("crossSelection")
       ,DT::DTOutput("cfdata")
       ,uiOutput("buttonsCF")
       ,HTML("&nbsp;")
       )
##~ fillCol(flex=c(NA,1)
      ##~ # ,selectInput("cfcode","Conservation Feature",cfmeta$label
      ##~ #             ,selected=sample(cfmeta$label,1),width="680px")
       ##~ ,DT::DTOutput('cfdata')
##~ )
```
```{r eval=F & isShiny}
output$crossSelection <- renderPrint({
   selectionTables()
})
```

```{r,eval=isShiny}
output$cfmeta <- renderText({
   captionCF()
})
```

```{r eval=isShiny & hlink}
output$cflink <- renderText({
   paste0("<a href=#section-cfmap>","Details","</a>")
})
```

```{r eval=isShiny}
output$cfdata <- DT::renderDT({
   tableCFdata()
})
```

```{r, eval=isShiny}
output$buttonsCF <- renderUI({
   buttonsCF()
})
```


## CF metadata and map {data-width=200}

### Cell Comment CF {data-height="auto"}

```{r eval=T & isShiny}
renderTable({
   cellComment()
})
```

### Industry Description {data-height=200}

```{r eval=T & isShiny}
renderUI({
   industry <- rvSelectIndustry()
   if (is.null(industry)) {
      renderImage(displayCF(),deleteFile=T)
   }
   else {
      industryDescription()
   }
})
#renderImage({
#   displayCF()
#},deleteFile=T)
```

```{r, eval=T & isShiny & staffOnly, results='asis'}
cat("### staff only CF {data-height=\"auto\"}\n\n")
renderPrint({
   selectionTables()
})
```

# Human Activity Details {#annualIndustry data-orientation="columns" `r if (hideTabs) ".hidden"`}

## {data-width=500}

### All compatibilities for a single Industry
```{r eval=T & isShiny}
fillCol(flex=c(NA,1,NA,NA)
       ##~ ,shiny::selectInput("cfcode","CF from crosstable",nameInit,width=width)
      # ,selectInput("industry","Industry"
      #             ,choices=nameInit
                  # ,selected=sample(cfmeta$label,1)
      #             ,width=width)
      # ,textOutput("crossCol")
      ##~ # ,htmlOutput('cflink')
       ,htmlOutput('industrymeta')
      # ,verbatimTextOutput("crossSelection")
       ,DT::DTOutput("industrydata")
       ,uiOutput("buttonsIndustry")
       ,HTML("&nbsp;")
       )
```

```{r, eval=isShiny}
output$industrymeta <- renderText({
   captionIndustry()
})
output$industrydata <- DT::renderDT({
   tableIndustryData()
})
output$buttonsIndustry <- renderUI({
   buttonsIndustry()
})
```

## Right column {data-width=200}

### Cell comment Industry {data-height="auto"}

```{r eval=T & isShiny}
renderTable({
   cellComment()
})
```

### Display CF {data-height=200}

```{r eval=T & isShiny}
renderUI({
   cf <- rvSelectCF()
  if (!is.null(cf)) {
      if (T)
         renderLeaflet({
            leafletCF(cf)
         })
      else
         renderImage({
            displayCF()
         },deleteFile=F)
   } else {
      renderUI({
         industryDescription()
      })
   }
})
```

```{r, eval=T & isShiny & staffOnly, results='asis'}
cat("### staff only CF {data-height=\"auto\"}\n\n")
renderPrint({
   selectionTables()
})
```


<!--
https://stackoverflow.com/questions/43225165/combine-in-flexdashboard-with-multiple-pages-different-types-of-vertical-layout
-->

# Reg desc {#descRegion data-orientation="columns" `r if (hideTabs) ".hidden"`}

## Column 1 - map {data-width=300}

### Region figures 

```{r}
fillCol(flex=c(1,NA,NA)
   ,leafletOutput("regionLeaflet")
  # ,uiOutput("uiRegionLeaflet")
   ##~ ,fixedRow(NULL
      ##~ ,column(6
         ##~ ,checkboxInput("regionDesc","Show Existing Protected Areas (it is not quick)")
      ##~ )
      ##~ ,column(3
         ##~ ,checkboxInput("switchNAO","Show NAO")
      ##~ )
      ##~ ,column(3
         ##~ ,checkboxInput("switchNAC","Show NAC")
      ##~ )
   ##~ )
   ,fixedRow(NULL
      ,column(4
         ,conditionalPanel(condition="input.initEPA>='0'"
           # ,actionLink("actionEPA","Show Existing Protected Areas")
            ,checkboxInput("actionEPA","Stats for Existing Protected Areas")
         )
      )
      ,column(4
         ,conditionalPanel(condition="input.initEPA=='0'"
            ,actionLink("initEPA","Show Existing Protected Areas")
         )
      )
      ,column(2
         ,conditionalPanel(condition="input.actionNAO=='0'"
            ,actionLink("actionNAO","Show NAO")
         )
      )
      ,column(2
         ,conditionalPanel(condition="input.actionNAC=='0'"
            ,actionLink("actionNAC","Show NAC")
         )
      )
   )
   ,renderUI({
      b1 <- navButton("Spatial query","#map",col="map",span=T)
      b2 <- navButton("Selected Area Details","#crosstable",col="cross",span=T)
      navButton(list(b1,b2))
   })
)
output$uiRegionLeaflet <- renderUI({
   req(input$actionRegion>0)
   ret <- leafletOutput("regionLeaflet")
   ret
})
output$regionLeaflet <- renderLeaflet({
   aoi <- isolate(rvAOI())
   regionAddAOI(aoi=aoi,addOverlay=TRUE)
})
```

## Column 2 Region Details {data-width=300}

### Basic Statistics {data-height="auto"}


```{r}
DT::renderDT({
   result <- rvRegionStats()
   res <- result[grep('^[a-zE]',names(result))] |> as.data.frame()
   cname <- colnames(res)
   indRound <- grep("^(pu|area|ePA)",colnames(res))
   cname[1] <- paste0("<abbr title='"
                     ,"Number of Planning Units in Selected Region(s)","'>"
                     ,"PUs","</abbr>")
   cname[2] <- paste0("<abbr title='"
                     ,"Number of Conservation Features","'>"
                     ,"CFs","</abbr>")
   cname[3] <- paste0("<abbr title='"
                     ,"Area of Selected Region(s), sq.km","'>"
                     ,"srcArea","</abbr>")
   cname[4] <- paste0("<abbr title='"
                     ,"Area of Planning Units in Selected Region(s), sq.km","'>"
                     ,"puArea","</abbr>")
   cname[5] <- paste0("<abbr title='"
                     ,"Terrestrial Area in Selected Region(s), sq.km","'>"
                     ,"puLand","</abbr>")
   cname[6] <- paste0("<abbr title='"
                     ,"Marine Area in Selected Region(s), sq.km","'>"
                     ,"puMarine","</abbr>")
   if (length(cname)>=7)
      cname[7] <- paste0("<abbr title='"
                        ,"Existing Protected Areas in Selected Region(s), sq.km","'>"
                        ,"EPA","</abbr>")
   colnames(res) <- cname
   da <- DT::datatable(res,escape=F,rownames="",selection="none"
                      ,options=list(dom="t",ordering=F),class="compact")
   DT::formatRound(da,indRound,1)
})
```

### {data-height=250}

```{r}
fillRow(flex=c(6,1)
   ,fillCol(flex=1
      ,renderPlotly({
         metrics <- rvRegionStats()
         result <- metrics$'IND'
         IND <- data.frame(industry=names(result),value=result)
         IND <- IND[order(IND$value,decreasing=TRUE),]
         IND$industry <- factor(IND$industry,levels=IND$industry,ordered=TRUE)
         iname <- substr(IND$industry,1,1)
         sname <- unique(iname)
         ct <- ursa::cubehelix(length(sname),bright=167,rotate="circle")
         names(ct) <- sname
         mcol <- ct[iname]
         mvalue <- meanNAC*metrics$nPU/length(IND$industry)
         p <- plot_ly(IND,x=~industry,y=~value,type="bar",orientation="v"
                     ,marker=list(color=mcol)
                     ) %>%
                  layout(NULL
                        ,xaxis=list(title=""),yaxis=list(title="IND")
                        ,showlegend=FALSE
                        ,shapes=list(list(x0=~head(industry,1),x1=~tail(industry,1)
                          ,y0=mvalue,y1=mvalue
                          ,type="line",line=list(color="#888",dash="dot")))
                       # ,margin=list(l=0,r=0,t=0)
                        )
         p
      })
   )
   ,fillCol(flex=c(NA,1,NA)
      ### <abbr title='Industries of concern'>TOP IND</abbr> {data-height="auto"}
      ,DT::renderDT({
         res <- rvRegionStats()[['TOP IND']] |> data.frame() |> t()
         cname <- colnames(res)
         lname <- industryName(cname)
         colnames(res) <- paste0("<abbr title='",lname,"'>",cname,"</abbr>")
         res <- t(res) |> as.data.frame(check.names=FALSE)
         da <- DT::datatable(res,escape=F
                            ,colnames="IND TOP"
                            ,selection="none"
                            ,options=list(dom="t",ordering=F),class="compact"
                           # ,width="200px"
                            )
         DT::formatRound(da,colnames(res),1)
      })
      ,HTML("&nbsp;&nbsp;&nbsp;&nbsp;")
      ### <abbr title='Industries of the least concern'>LC IND</abbr> {data-height="auto"}
      ,DT::renderDT({
         res <- rvRegionStats()[['LC IND']] |> data.frame() |> t()
         cname <- colnames(res)
         lname <- industryName(cname)
         colnames(res) <- paste0("<abbr title='",lname,"'>",cname,"</abbr>")
         res <- t(res) |> as.data.frame(check.names=FALSE)
         da <- DT::datatable(res,escape=F
                            ,colnames="LC IND"
                            ,selection="none"
                            ,options=list(dom="t",ordering=F),class="compact"
                            ,width="200px"
                            )
         DT::formatRound(da,colnames(res),1)
      })
   )
  # ,HTML("&nbsp;&nbsp;&nbsp;&nbsp;")
)
```

### {data-height=150}

```{r}
fillRow(flex=c(1,NA,2,1)
   ,DT::renderDT({
      result <- rvRegionStats()
      res <- result[grep('^NA',names(result))] |> as.data.frame()
      cname <- colnames(res)
      cname[cname=="NAO"] <- paste0("<abbr title='"
                                   ,"Conservation concern, not allowed only"
                                   ,"'>","NAO","</abbr>")
      cname[cname=="NAC"] <- paste0("<abbr title='"
                                   ,"Conservation concern, not allowed and conditional"
                                   ,"'>","NAC","</abbr>")
      cname[cname=="NAOR"] <- paste0("<abbr title='"
                                   ,"Conservation concern, not allowed only relative"
                                   ,"'>","NAOR","</abbr>")
      cname[cname=="NACR"] <- paste0("<abbr title='"
                                   ,"Conservation concern, not allowed and conditional relative"
                                   ,"'>","NACR","</abbr>")
      colnames(res) <- cname
      res <- t(res) |> as.data.frame(check.names=FALSE)
      da <- DT::datatable(res,escape=F
                         ,colnames=""
                         ,selection="none"
                         ,options=list(dom="t",ordering=F),class="compact"
                         ,width="200px"
                         )
      DT::formatRound(da,colnames(res),1)
   })
   ,HTML("&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;")
   ,renderPlotly({
      sc <- rvRegionStats()[['SC0']]
      sc <- data.frame(month=names(sc),value=sc)
      sc$month <- factor(sc$month,levels=sc$month,ordered=TRUE)
      p <- plot_ly(sc,x=~month,y=~value,type="bar",orientation="v") %>%
               layout(NULL
                     ,xaxis=list(title=""),yaxis=list(title="SC IND")
                    # ,margin=list(l=0,r=0,t=0)
                     )
      p
   })
   ,DT::renderDT({
      res <- rvRegionStats()[['SC']] |> data.frame() |> t()
      res <- t(res) |> as.data.frame(check.names=FALSE)
      da <- DT::datatable(res,escape=F
                         ,colnames="<abbr title='Season of concern'>SC</abbr>"
                         ,selection="none"
                         ,options=list(dom="t",ordering=F),class="compact")
      DT::formatRound(da,colnames(res),1)
   })
)
```

### {data-height="auto"}

```{r}
downloadLink("downloadMetrics","Download interim tables for NAO and NAC")
HTML("&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;")
downloadLink("instantReport","Instant Report")
output$downloadMetrics <- downloadHandler(
   filename=function() {
      aoi <- rvAOI()
      if (is.null(aoi))
         return("Global metrics.xlsx")
      lab <- regionSF[[input$region]]$region[aoi$id]
      paste0(lab," metrics.xlsx")
   }
   ,content=function(file) {
      interim <- rvRegionMetrics()
     # str(interim)
      dNAO <- cbind(interim$cover,interim$NAO)
      dNAC <- cbind(interim$cover,interim$NAC)
     # str(res)
     # res <- iris
      xlsx::write.xlsx(dNAO,file,sheetName="NAO",append=FALSE)
      xlsx::write.xlsx(dNAC,file,sheetName="NAC",append=TRUE)
   }
)
output$instantReport <- downloadHandler(
   filename=function() {
      aoi <- rvAOI()
      if (is.null(aoi))
         lab <- "Global"
      lab <- regionSF[[input$region]]$region[aoi$id]
      paste0("metrics-",digest::digest(lab,"crc32"),".pdf")
   }
   ,content=function(file) {
      cat("instantReport (content):\n")
      interim <- rvRegionMetrics()
      str(interim)
      print(getwd())
      fname <- "report/instantReport.Rmd"
      # tempReport <- file.path(tempdir(),fname)
     # file.copy(fname,tempReport,overwrite=TRUE)
      showModal(modalDialog(title = "Compiling in progress","Please wait"
                       ,size="s",easyClose = TRUE,footer = NULL))
      ret <- rmarkdown::render(fname
                       ,output_file=file
                       ,output_format=bookdown::pdf_document2(toc=FALSE
                          ,number_sections=FALSE
                       )
                       ,params=list(metrics=interim,aoi=rvAOI())
                       ,envir=new.env(parent=globalenv()))
      removeModal()
      ret
   }
)
```
 
# CF desc {#descCF .zzzhidden data-orientation="columns" `r if (hideTabs) ".hidden"`}

## {data-width=300}

### Metadata

```{r eval=T & isShiny}
fillCol(flex=c(NA,1,1)
   ,renderTable({
      metadataCF()
   })
   ,renderUI({
      b <- buttonsTemplate()
      b <- b[grep("cf.*overview",names(b),invert=TRUE)]
      navButton(b)
   })
   ,if (staffOnly) renderPrint({
      selectionTables()
   }) else HTML("&nbsp;")
)
```

## {data-width=500}

### Map

```{r eval=T & isShiny}
  # renderImage(displayCF(),deleteFile=T)
   renderLeaflet(leafletCF())
```

# I desc {#descIndustry .zzzhidden data-orientation="columns" `r if (hideTabs) ".hidden"`}

## {data-width=500}

### Industry map 

```{r eval=T & isShiny}
if (staffOnly) {
   fillCol(flex=c(1,NA,NA)
      ,leafletOutput("industryMap")
      ,checkboxInput("industryDesc","Show map (it is not quick)",value=FALSE)
     # ,actionLink("industryDesc","Show map (it is not quick)")
      ,renderPrint(selectionTables())
   )
} else {
   fillCol(flex=c(1,NA)
      ,leafletOutput("industryMap")
      ,checkboxInput("industryDesc","Show map (it is not quick)",value=FALSE)
     # ,actionLink("industryDesc","Show map (it is not quick)")
   )
}
output$industryMap <- renderLeaflet({
   req(input$industryDesc)
   displayIndustry()
})
```


## {data-width=300}

### Industry description


```{r eval=T & isShiny}
fillCol(flex=c(1,NULL,NA)
   ,renderUI({
      industryDescription()
   })
   ##~ ,if (staffOnly) renderPrint(
      ##~ selectionTables()
   ##~ )
   ,renderUI({
      b <- buttonsTemplate()
      b <- b[grep("indus.*overview",names(b),invert=TRUE)]
      navButton(b)
   })
)
```

# Lists... {#list data-orientation="rows" `r if (hideTabs) ".hidden"`}

## {data-height="auto"}

### Conservation Features

```{r, eval=T & isShiny}
fillCol(flex=1,DT::DTOutput("onlyCF"))
output$onlyCF <- DT::renderDT({
   tableOnlyCF()
})
```

```{r, eval=F & isShiny}
output$switchCF <- renderUI({
   switchCF()
})
```

### Human use in the Arctic

```{r, eval=T & isShiny}
fillCol(flex=1,DT::DTOutput("onlyIndustry"))
output$onlyIndustry <- DT::renderDT({
   tableOnlyIndustry()
})
```

```{r, eval=F & isShiny}
output$switchIndustry <- renderUI({
   switchIndustry()
})
```

## {data-height=50}
   
```{r, eval=isShiny}
fillCol(flex=1,uiOutput("buttonsList"))
output$buttonsList <- renderUI({
   buttonsList()
})
```

```{r, eval=T, child="include/welcome.Rmd"}
```

### Staff only quick navigation {data-width=100}

[Spatial Query](#map)  
[Cross details](#crosstable)  
[CF details](#annualCF)  
[Industry details](#annualIndustry)  
[CF overview](#descCF)     
[Industry overview](#descIndustry)  
[Region overview](#descRegion)  
[Lists CF and Indutries](#list)  

----

```{r, eval=F}
sliderInput("omitPercent",label="Omit small coverage",min=0,max=10,step=0.1,value=0)
```
