---
params:
  metrics: NULL
  aoi: NULL
  kind: 0
  dpath: "./requests"
pagetitle: Geranium instant report
title: Geranium instant report
author: Boris Solovyev, Nikita Platonov
date: "`r as.POSIXlt(Sys.time())`"
bibliography1: ./demography.bib
link-citations: true
csl: https://nplatonov.github.io/platt4.csl
output1:
   bookdown::pdf_document2:
      toc: false
      number_sections: false
   bookdown::html_document2:
      base_format: rmarkdown::html_vignette
      css: https://nplatonov.github.io/html_vignette.css
      lib_dir: "`r params$dpath`"
      self_containded: false
      number_sections: no
   pdf_document:
      fig_caption: false
   html_fragment: #
---

```{r setup,include=FALSE}
aoi <- params$aoi
metrics <- params$metrics
dpath <- params$dpath
knitr::opts_chunk$set(fig.align="center",fig.width=6,fig.height=4.8
                     ,widgetframe_widgets_dir=params$dpath
                     ,echo=F,message=F,warning=F
                     )
file.remove(dir(path=dpath,pattern="^orca.+\\.(pdf|png)$",full.names=TRUE,recursive=TRUE))
require(plotly)
```

```{r eval=T,include=F}
filetype <- knitr::opts_knit$get("rmarkdown.pandoc.to")
'publish' <- function(p) {
   if (inherits(p,"ggplot")) {
      ret <- p
   }
   else if (inherits(p,"plotly")) {
      if (filetype %in% "latex") {
         if (!dir.exists(params$dpath))
            dir.create(params$dpath,recursive=TRUE)
         if (TRUE) {
            fs <- 18
            p <- plotly::layout(p
                               ,title=list(font=list(size=fs))
                               ,legend=list(font=list(size=round(0.9*fs)))
                               ,xaxis=list(tickfont=list(size=fs),titlefont=list(size=fs))
                               ,yaxis=list(tickfont=list(size=fs),titlefont=list(size=fs))
                               )
         }
        # if (FALSE) { 
        #    opW <- options(warn=-10)
        #    ret <- plotly::export(p)
        #    options(opW)
        # }
         if (nchar(Sys.which("ZZZorca"))) {
            fileout <- file.path(params$dpath,basename(tempfile(pattern="orca",fileext=".pdf")))
            plotly::orca(p,fileout)
            ret <- knitr::include_graphics(fileout)
         }
         else {
            fileout <- file.path(params$dpath,basename(tempfile(pattern="orca",fileext=".png")))
            ret <- NULL
            if (F) {
               ret <- try(plotly::plotly_IMAGE(p,width=800,height=600,scale=1,out_file=fileout))
               if (!inherits(ret,"try-error"))
                  ret <- knitr::include_graphics(fileout,dpi=150)
               else
                  ret <- NULL
            }
            if (is.null(ret)) {
               opW <- options(warn=-10)
               ret <- plotly::export(p)
               options(opW)
            }
         }
      }
      else
         ret <- p
   }
   ret
}
```

```{r, code=readLines("instantReport.R")}
```

```{r, eval=T}
if (is.null(aoi)) {
   aoi <- regionSF[[c("PACs","LMEs")[2]]]
   aoi <- aoi[grep("(\\s(22)|Barents)",aoi$region),]
}
if (is.null(metrics)) {
   group <- c("\\d")
   ctable <- crosstable(aoi=aoi,group=group)
   metrics <- regionStats(aoi=aoi,ctable=ctable,raw=T)
}
if ("result" %in% names(metrics)) {
   general <- metrics
   metrics <- general$result
} else {
   general <- NULL
}
isAOI <- is_spatial(aoi)
if (isAOI) {
   if ("id" %in% spatial_colnames(aoi))
      lab <- regionSF[[aoi$region[1]]]$region[aoi$id]
   else
      lab <- aoi$region
   if (is.null(lab))
      lab <- "Custom Selection"
   if (length(lab)>1)
      lab <- paste(lab,sep=", ")
}
```

## Instant report for `r lab`.

This is dynamically generated report based on passed parameters.


```{r selectional, fig.cap="Selection"}
gaoi <- ursa:::spatialize(spatial_geometry(aoi),resetGrid=TRUE)
compose_open()
panel_new("white")
ct1 <- panel_plot(sf::st_cast(spatial_union(puAOI(aoi)),"MULTILINESTRING"),lwd=1)
ct2 <- panel_plot(gaoi)
ursa:::panel_legend(list('Gridded (PUs) selection'=ct1,'Original selection'=ct2))
panel_decor(coast.fill="#00000010")
knitr::include_graphics(compose_close())
```

The area of selected region is `r format(round(metrics$area_src,-1))` km^2^.
This selected area is inscribed into `r format(round(metrics$nPU,0))` planning units (PUs).
Selected area outside of PUs domain is ignored.
Cellulared (gridded) selection is `r format(round(metrics$area_pu,-1))` km^2^.
For this gridded selection `r format(round(metrics$puMarine,-1))` km^2^ are aquatories,
and `r format(round(metrics$puLand,-1))` km^2^ are territories.
`r if (!is.null(metrics$ePA)) paste("Existing protected areas occupy",format(round(metrics$ePA,-1)),"km^2^ in selected area.")`

```{r}
da <- metrics[grep("^NA",names(metrics))] |> as.data.frame() |> t() |> as.data.frame()
rname <- dname <- rownames(da)
dname[rname=="NAC"] <- "Conservation concern, not allowed and conditional"
dname[rname=="NAO"] <- "Conservation concern, not allowed only"
dname[rname=="NAOR"] <- "Conservation concern, not allowed only relative"
dname[rname=="NACR"] <- "Conservation concern, not allowed and conditional relative"
da <- cbind(name=dname,da)
knitr::kable(da,col.names=NULL,caption="Principal concern indices")
```


```{r}
cf <- rownames(general$cover)
gr <- sort(unique(substr(cf,1,1)))
cfgroup <- groupList[match(gr,names(groupList))]
icode <- names(metrics$'IND')
iname <- industryName(icode)
uiname <- unlist(industries)
igroup <- unique(gsub("\\d+$","",names(uiname[match(iname,uiname)])))
```

There are `r metrics$nCF` conservation features (CFs) in selection.
They represent `r paste(unname(dQuote(cfgroup)),sep=", ")` `r ifelse(length(cfgroup)==1,"group","groups")` of CFs.
Industries represent `r paste(dQuote(igroup),sep=", ")` activity `r ifelse(length(igroup)==1,"group","groups")`.

```{r residential, fig.cap="Leading residential CFs in selection"}
da <- data.frame(cf=rownames(general$cover),value=general$cover$Cover)
da <- da[order(da$value,decreasing=TRUE),]
da$cf <- factor(da$cf,levels=da$cf,ordered=TRUE)
#ind <- which(da$value==1)
da <- head(da,32)
p <- plot_ly(da,x=~cf,y=~value,type="bar")
publish(p)
```

```{r industrial, fig.cap="Industrial concern"}
IND <- data.frame(industry=names(metrics$'IND'),value=metrics$'IND')
IND <- IND[order(IND$value,decreasing=TRUE),]
IND$industry <- factor(IND$industry,levels=IND$industry,ordered=TRUE)
p <- plot_ly(IND,x=~industry,y=~value,type="bar",orientation="v") %>%
         layout(NULL
               ,xaxis=list(title=""),yaxis=list(title="IND")
              # ,margin=list(l=0,r=0,t=0)
               )
publish(p)
```

```{r seasonal, fig.cap="Seasonal concern"}
sc <- data.frame(month=names(metrics$'SC0'),value=metrics$'SC0')
sc$month <- factor(sc$month,levels=sc$month,ordered=TRUE)
p <- plot_ly(sc,x=~month,y=~value,type="bar") %>%
         layout(NULL
               ,xaxis=list(title=""),yaxis=list(title="SC IND")
              # ,margin=list(l=0,r=0,t=0)
               )
publish(p)
```

```{r topind}
da <- data.frame(name=names(metrics$'TOP IND'),value=metrics$'TOP IND')
#da$name <- paste0(industryName(da$name)," (",da$name,")")
da$name <- industryName(da$name)
colnames(da) <- c("Industry","Concern")
knitr::kable(da,caption="Industries of concern (TOP IND)")
```

```{r lcind}
da <- data.frame(name=names(metrics$'LC IND'),value=metrics$'LC IND')
#da$name <- paste0(industryName(da$name)," (",da$name,")")
da$name <- industryName(da$name)
colnames(da) <- c("Industry","Concern")
knitr::kable(da,caption="Industries of least concern (LC IND)")
```

```{r scind}
da <- data.frame(value=metrics$'SC')
colnames(da) <- c("Concern")
knitr::kable(da,caption="Seasons of concern (SC)")
```

```{r}
# str(aoi)
```

```{r}
# str(metrics)
```

```{r}
# str(general)
```
